Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-25 analysis/paper/paper.Rnw
completed parts of DESCRIPTION

<<load-broman>>=
library(broman)
@

@@

<<more_setup-2>>=
hot_lower <- hot_mid - 2
hot_upper <- hot_mid + 2
fp <- paste0("../figures/Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = fp)
@

<<readRDS-2>>=
pleio_mixed_list <- readRDS(paste0("_cache/Chr", hot_chr, "_pleio.rds"))
pleio_local_list <- readRDS(paste0("_cache/Chr", hot_chr, "_pleio_local.rds"))
pleio_nonlocal_list <- readRDS(paste0("_cache/Chr", hot_chr, "_pleio_nonlocal.rds"))
med_list <- readRDS(paste0("_cache/Chr", hot_chr, "_mediations.rds"))
@

>>>>

<<load-broman>>=
library(broman)
library(here)
@

@@

<<more_setup-2>>=
hot_lower <- hot_mid - 2
hot_upper <- hot_mid + 2
fp <- paste0("Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = here("analysis", "figures", fp))
@

<<readRDS-2>>=
pleio_mixed_list <- readRDS(here("analysis", "data", paste0("Chr", hot_chr, "_pleio.rds")))
pleio_local_list <- readRDS(here("analysis", "data", paste0("Chr", hot_chr, "_pleio_local.rds")))
pleio_nonlocal_list <- readRDS(here("analysis", "data", paste0("Chr", hot_chr, "_pleio_nonlocal.rds")))
med_list <- readRDS(here("analysis", "data", paste0("Chr", hot_chr, "_mediations.rds")))
@
